---
title: "P8105 Homework 6"
author: "Junxian Chen (jc5314)"
date: "11/15/2019"
output: github_document
---

```{r, include = FALSE}
library(tidyverse)
library(glmnet)
library(modelr)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
  message = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
theme_set(theme_gray(base_size = 10) + theme(legend.position = "bottom"))
```

# Problem 1

Firstly, read in the dataset and do data manipulation.

```{r}
birthweight_dat = 
  read_csv("./data/birthweight.csv") %>% 
  mutate(
    babysex = factor(babysex, levels = c('1', '2')),
    frace = factor(frace, levels = c('1', '2', '3', '4', '8', '9')),
    malform = factor(malform, levels = c('0', '1')),
    mrace = factor(mrace, levels = c('1', '2', '3', '4', '8'))
  )
```

Use the **stepwise regreession method** to do the model selection.

```{r}
model_fit = lm(bwt ~ ., data = birthweight_dat) %>% 
  step(direction = 'backward')

summary(model_fit)
```

**Describe your modeling process:**


A plot showing model residuals against fitted values: 

```{r}
birthweight_dat %>% 
  add_predictions(model_fit) %>% 
  add_residuals(model_fit) %>% 
  ggplot(aes(x = pred, y = resid)) +
  geom_point(alpha = .4, size = 2) +
  xlab("Fitted Values") +
  ylab("Residuals")
```

Model using length at birth and gestational age as predictors (main effects only):

```{r}
model_fit2 = lm(bwt ~ blength + gaweeks, data = birthweight_dat)

model_fit2 %>% broom::tidy() %>% knitr::kable()
```

Model using head circumference, length, sex, and all interactions (including the three-way interaction) between these:

```{r}
model_fit3 = lm(bwt ~ bhead * blength * babysex, data = birthweight_dat)

model_fit3 %>% broom::tidy() %>% knitr::kable()
```

```{r}
cv_df = 
  crossv_mc(birthweight_dat, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)
    )
```

```{r}
cv_df = 
  cv_df %>% 
  mutate(model1  = map(train, ~lm( bwt ~ babysex + bhead + blength + delwt + fincome + gaweeks + mheight + mrace + parity + ppwt + smoken, data = .x)),
         model2  = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
         model3  = map(train, ~lm(bwt ~ bhead * blength * babysex, data = .x))) %>% 
  mutate(rmse_model1 = map2_dbl(model1, test, ~rmse(model = .x, data = .y)),
         rmse_model2 = map2_dbl(model2, test, ~rmse(model = .x, data = .y)),
         rmse_model3 = map2_dbl(model3, test, ~rmse(model = .x, data = .y)))
```

```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```

