---
title: "P8105 Homework 6"
author: "Junxian Chen (jc5314)"
date: "11/15/2019"
output: 
  github_document:
    pandoc_args: --webtex
---

```{r, include = FALSE}
library(tidyverse)
library(glmnet)
library(modelr)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
  message = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
theme_set(theme_gray(base_size = 10) + theme(legend.position = "bottom"))
```


# Problem 1

Firstly, read in the dataset and do data manipulation.

```{r}
birthweight_dat = 
  read_csv("./data/birthweight.csv") %>% 
  mutate(
    babysex = factor(babysex, levels = c('1', '2')),
    frace = factor(frace, levels = c('1', '2', '3', '4', '8', '9')),
    malform = factor(malform, levels = c('0', '1')),
    mrace = factor(mrace, levels = c('1', '2', '3', '4', '8'))
  )
```

Use the **stepwise regreession method** to do the model selection.

```{r}
model_fit = lm(bwt ~ ., data = birthweight_dat) %>% 
  step(direction = 'backward')

summary(model_fit)
```

**Describe your modeling process:**


A plot showing model residuals against fitted values: 

```{r}
birthweight_dat %>% 
  add_predictions(model_fit) %>% 
  add_residuals(model_fit) %>% 
  ggplot(aes(x = pred, y = resid)) +
  geom_point(alpha = .4, size = 2) +
  xlab("Fitted Values") +
  ylab("Residuals")
```

Model using length at birth and gestational age as predictors (main effects only):

```{r}
model_fit2 = lm(bwt ~ blength + gaweeks, data = birthweight_dat)

model_fit2 %>% broom::tidy() %>% knitr::kable()
```

Model using head circumference, length, sex, and all interactions (including the three-way interaction) between these:

```{r}
model_fit3 = lm(bwt ~ bhead * blength * babysex, data = birthweight_dat)

model_fit3 %>% broom::tidy() %>% knitr::kable()
```

Make comparisons in terms of the cross-validated prediction error.

```{r}
cv_df = 
  crossv_mc(birthweight_dat, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)
    )
```

```{r}
cv_df = 
  cv_df %>% 
  mutate(model1  = map(train, ~lm( bwt ~ babysex + bhead + blength + delwt + fincome + gaweeks + mheight + mrace + parity + ppwt + smoken, data = .x)),
         model2  = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
         model3  = map(train, ~lm(bwt ~ bhead * blength * babysex, data = .x))) %>% 
  mutate(rmse_model1 = map2_dbl(model1, test, ~rmse(model = .x, data = .y)),
         rmse_model2 = map2_dbl(model2, test, ~rmse(model = .x, data = .y)),
         rmse_model3 = map2_dbl(model3, test, ~rmse(model = .x, data = .y)))
```

```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```

**Comment:**


# Problem 2

Import data from website:

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

```{r}
boot_straps = weather_df %>% 
  bootstrap(n = 5000) %>% 
  mutate(
    models = map(strap,~ lm(tmax ~ tmin, data = .x) ),
    results = map(models, broom::tidy),
    results_glance = map(models, broom::glance)) %>% 
  select(-strap, -models) %>% 
  unnest(results, results_glance) %>% 
  select(.id, term, estimate, r.squared) %>% 
  pivot_wider(
    names_from = "term",
    values_from = "estimate"
  ) %>% 
  janitor::clean_names() %>% 
  mutate(
    log_coef = log(intercept * tmin)
  )

boot_straps
```

Plot of the distribution of $\hat{r}^2$:

```{r}
boot_straps %>% 
  ggplot(aes(x = r_squared)) +
  geom_density() +
  xlab("Estimated r squared")
```

Plot of the distribution of $log(\hat{\beta}_0*\hat{\beta}_1)$:

```{r}
boot_straps %>% 
  ggplot(aes(x = log_coef)) +
  geom_density() +
  xlab("Log(Beta_0 x Beta_1)")
```

2.5% and 97.5% quantiles for $\hat{r}^2$:

```{r}
boot_straps %>% 
  pull(r_squared) %>% 
  quantile(c(0.025, 0.975))
```

2.5% and 97.5% quantiles for $log(\hat{\beta}_0*\hat{\beta}_1)$:

```{r}
boot_straps %>% 
  pull(log_coef) %>% 
  quantile(c(0.025, 0.975))
```

